|

### 2021-11-09 submission/manuscript.rmd
fix plots and continue results section

The model including a constant relative treatment effect had the
lowest median RMSE in scenarios with a true constant relative
treatment effect (OR = 0.8, N = `r 4250` and AUC = 0.75) or with
moderate linear deviations (Supplement, Figure XX). However, when we
considered deviations from constant relative treatment effects, the
linear interaction model performed best most of the time, with RCS-3
having very comparable performance, outperforming the former in the
case of strong treatment-related harms and non-monotonic
deviations. The adaptive approach had comparable performance to the
best-performing method in each scenario, however, we observed
increased variability in the case of linear and non-monotonic
deviations, especially for moderate or strong treatment-related
harms.

The adaptive approach selected the constant treatment effect model
`r adaptiveSelections %>% filter(scenarioId == 217) %>% pull(treatment) * 100`\% 
of the time, when no constant treatment-related harms were
considered, which dropped to
`r adaptiveSelections %>% filter(scenarioId == 219) %>% pull(treatment) * 100`\% 
in the case of strong treatment-related harms. When strong linear
deviations were considered, the adaptive approach favored the constant
treatment effect model
(`r adaptiveSelections %>% filter(scenarioId == 289) %>% pull(treatment) * 100`\%
of the time) in the absence of treatment-related harms, which was
replaced mainly by the linear interaction model (from
`r adaptiveSelections %>% filter(scenarioId == 289) %>% pull(risk) * 100`\%
to 
`r adaptiveSelections %>% filter(scenarioId == 291) %>% pull(risk) * 100`\%
of the time) with increasing treatment-related harms. In the case of
strong quadratic deviations, the adaptive approach selected the
linear interaction model the majority of the time which also increased
with stronger treatment-related harms (from
`r adaptiveSelections %>% filter(scenarioId == 361) %>% pull(risk) * 100`\%
with no harms to
`r adaptiveSelections %>% filter(scenarioId == 363) %>% pull(risk) * 100`\%
with strong harms ). RCS-3 selection frequency decreased with stronger
treatment-related harms (from
`r adaptiveSelections %>% filter(scenarioId == 361) %>% pull(rcs_3) * 100`\%
with no harms to
`r adaptiveSelections %>% filter(scenarioId == 363) %>% pull(rcs_3) * 100`\%
with strong harms ). Finally, with true non-monotonic deviations the
adaptive approach mainly selected the constant treatment effect model
(from
`r adaptiveSelections %>% filter(scenarioId == 397) %>% pull(treatment) * 100`\%
with no harms to
`r adaptiveSelections %>% filter(scenarioId == 399) %>% pull(treatment) * 100`\%
with strong harms), the linear interaction model (from
`r adaptiveSelections %>% filter(scenarioId == 397) %>% pull(risk) * 100`\%
with no harms to
`r adaptiveSelections %>% filter(scenarioId == 399) %>% pull(risk) * 100`\%
with strong harms) and the RCS-3 model
(from
`r adaptiveSelections %>% filter(scenarioId == 397) %>% pull(rcs_3) * 100`\%
with no harms to
`r adaptiveSelections %>% filter(scenarioId == 399) %>% pull(rcs_3) * 100`\%
with strong harms). For more details, see Supplement Table XX).

@@

When we increased the sample size (N = `r 17000`), the model including
a constant relative treatment effect had the lowest RMSE under the
assumption of true constant relative treatment effects (Figure
\ref{fig:rmsesamplesize}; Panel A). However, when introducing strong
linear deviations the linear interaction model outperformed the
constant treatment effect model (Figure \ref{fig:rmsesamplesize};
Panel B). Furthermore, the linear interaction model was outperformed
by the more flexible RCS models (3 knots) in the case of strong
quadratic and non-monotonic deviations. Again, the increased
flexibility of RCS smoothing with higher number of knots resulted in
overfitting and worse predictive accuracy (Figure
\ref{fig:rmsesamplesize}; Panels C and D). The adaptive approach again
followed the performance of the best performing models in each
scenario. In addition, the increased variability in the adaptive
method's errors in the base scenario disappeared with large sample
size.

>>>>

The linear interaction model outperformed all RCS methods in terms of
RMSE in scenarios with true constant relative treatment effect (OR =
0.8, N = `r 4250` and AUC = 0.75), strong linear and even strong
quadratic deviations (Figure \ref{fig:rmsebase}). However, with
non-monotonic deviations errors of the linear interaction model
increased substantially, especially in the presence of
treatment-related harms. In these scenarios, RCS-3 proved to be quite
robust outperforming all other methods. The constant treatment effect
approach had overall best performance under true constant treatment
effect settings, but was sensitive to all considered deviations,
resulting in increased error rates. Finally, the adaptive approach had
comparable performance to the best-performing method in each
scenario. However, we observed increased variability in the case of
linear and non-monotonic deviations, especially for moderate or strong
treatment-related harms.

In the case of true constant relative treatment effects, the adaptive
approach selected the constnant effect model the majority of the time,
even in the presence of treatment-related harms
(`r adaptiveSelections %>% filter(scenarioId == 217) %>% pull(treatment) * 100`\%
of the time with no harms to
`r adaptiveSelections %>% filter(scenarioId == 219) %>% pull(treatment) * 100`\% 
with strong harms). With strong linear or quadratic deviations and
increasing treatment-related harms the adaptive approach increasingly
favored the linear interaction model. In the case of true
non-monotonic deviations, we observed increasing selection frequencies
for RCS-3 with increasing treatment harms (from
`r adaptiveSelections %>% filter(scenarioId == 397) %>% pull(rcs_3) * 100`\%
with no harms to
`r adaptiveSelections %>% filter(scenarioId == 399) %>% pull(rcs_3) * 100`\%
with strong harms), whereas selection frequencies for the linear
interaction model dropped from
`r adaptiveSelections %>% filter(scenarioId == 397) %>% pull(risk) * 100`\%
with no harms to
`r adaptiveSelections %>% filter(scenarioId == 399) %>% pull(risk) * 100`\%
with strong harms. Finally, in the case of strong linear and
non-monotonic deviations selection frequencies of the constant
treatment effect model remained high despite increasing treatment
harms (Supplement, Table XX).

@@

Increasing the sample size to `r 17000` favored the RCS-3 approach the
most, as it achieved lowest or close to lowest RMSE across all
scenarios (Figure \ref{fig:rmsesamplesize}). Especially in cases of
strong quadratic and non-monotonic deviations RCS-3 had lower error
rates compared to the linear interaction approach, regardless of
treatment-related harms strength. The issues with the large error
variability of the adaptive approach improved with larger sample
sizes.
